---
title: "April 20 - Turning in Final Report Document"
output: html_document
author: "Matthew Distell, Bo Aldridge, Haris Adnan, Lucan Franzblau, Devin Obee"
date: "4-19-2022"
date: "2-25-2022"
output:
  pdf_document: default
  word_document: default
subtitle: 'due April 20, 2022 by 11:59 PM '
---


## Load Packages 
```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse) 
library(tidymodels)
install.packages("readxl")

``` 


# Load Data
```{r load-data, message = F}
myMovieData <- read_csv("IMDB-Movie-Data.csv")

```



## Introduction: Motivation and Context for the Research

Movies and film have served not only as a form of entertainment in the modern
era, but a reflection of who we are as a society, and what our culture values. 
Analyzing not only films themselves, but the broader types of films that succeed
can grant us many insights into our collective psyche.

One interesting idea that we sought to research was the difference between the 
preferences of fans and critics for a variety of metrics. The two main research 
questions, that we will dive into later, center around the differences between 
fans and critics with regards to genre preference and box office success.

This dichotomy is fascinating because it represents a cultural difference 
between factions of our society. While the average American might view certain
types of movies as entertaining or meaningful, those who call themselves 
"critics" might very well come from a far different background than the average
American, and thus carry a different persepetive. Analyzing these differences
can illuminate broader social and cultural differences in our country.



## Dataset

This dataset is from a csv called "IMDB-Movie-Data.csv". It was loaded into
this project as "myMovieData."

```{r movie data}
glimpse(myMovieData)
```

This myMovieData set contains the title, genre, description, director, actors,
year of release, runtime, fan rating from iMDB (International Movie Database)
(Rating), number of fan votes, box office revenue, and critic rating (Metascore) 
for 1000 movies. 


## Research Questions

From these broader ideas regarding movies and the relationships between 
certain types of them, we narrowed our research into two specific areas:


1. What is the relationship between fan ratings and critic ratings with regards
to box office success? Do higher fan or critic ratings lead to more box office
success? And if so, which factor contributes more?

2. What is the relationship between fan ratings and critic ratings with regards
to certain genres of movies? Specifically, is there any difference between how
fans and critics view, for example, action movies, or dramas?


## Methodology Part 1

Before getting started, we wanted to only look at "popular" movies. We 
arbitrarily defined this as having over 8000 reviews on the iMDB database.
Those movies with lower than that total are filtered out. This excluded 
133 of the initial 1000 movies from myMovieData.

Next, we created a new variable called newRating, which adjusts the "out-of-10"
scale value of the iMDB rating, and puts it on an "out-of-100" scale, similar
to that of the Metacritic scoring. 

```{r popular movie filter}
popularMovies <- myMovieData %>% 
  filter(Votes >= 8000)
```

```{r IMDB}
popularMovies <- popularMovies %>% 
  mutate(newRating = Rating * 10)
```


## Part 1: The Relationship Between Fans vs. Critic Scoring and Box Office Revenue

```{r}
cor.test(popularMovies$newRating, popularMovies$`Revenue (Millions)`,
  method = "spearman"
)
```

```{r}
cor.test(popularMovies$Metascore, popularMovies$`Revenue (Millions)`,
  method = "spearman"
)
```



```{r linearReg}
model1 <- linear_reg() %>%
  set_engine("lm") %>%
  fit(`Revenue (Millions)` ~ newRating + Metascore, data = popularMovies)
tidy(model1)
```




```{r}
popularMovies %>% 
  ggplot(aes(x = newRating, y = `Revenue (Millions)`)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Fan Ratings vs. Box Office Totals")
  
```

```{r}
popularMovies %>% 
  ggplot(aes(x = Metascore, y = `Revenue (Millions)`)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Critic Ratings vs. Box Office Totals")
  
```

## Part 1 Results and Discussion

In our correlation model, we found that there was a stronger relationship
between fan ratings and box office success (.137) as compared to critic ratings 
and box office success (.082). 

Our linear model confirms some of these findings. The null hypothesis for each 
parameter in this model is that each specific parameter does not
have a relationship with the box office revenue of each specific movie.

The alternative hypothesis, on the other hand, is that each specific parameter 
does have a relationship with the box office revenue of each specific movie.

The formula for our linear model is as follows:

$$\widehat{Revenue} = -83.8 + 2.39~fanRating + 
0.15criticRating  $$

The only predictor that was significant at the alpha level of .05 was newRating, 
with a p-value of .00006 and a high t-value. 

The newRating slope indicates that with all else held constant, for each 1 unit 
this movie increases in rating, the movie will earn, on average, $2.39 million 
more at the box office. The criticRating slope indicates that with all else held 
constant, for each 1 unit this movie increases in rating, the movie will earn, 
on average, $0.15 million more at the box office.

This does not necessarily mean that the other predictor, Metascore, was
uncorrelated with the outcome, but it does mean that once you account for the 
one factor that was statistically significant (newRating), the Metascore 
predictor in it of itself was not making as large of a difference there. 
Metascore predictor failed to reject the null hypothesis, while newRating
rejected the Null Hypothesis. 

Graphically, these same findings can be seen as well. There is a slightly 
stronger/similar positive correlation between newRating and box office as 
compared to Metascore and box office graphically. This, however,
does not take into account the fact that thep-value was not found to be 
ignificant, meaning that while there still is a positive trend between 
Metascore and box office, we cannot comment on its specific strength of 
relation to box office with nearly as much certainty as we can with user 
ratings in newRating. 

These findings, logically, make sense. The fact that there is not only a 
stronger correlation, but also a more statistically significant one between
fan ratings and box office success makes sense given that fans using these 
rating services should, as a whole, represent a larger portion of the 
population, which would, in turn, represent a larger portion of the 
ticket-purchasing constituency as compared to critics, who might come from a 
less diverse background (many critics might have gone to film/art school, or 
have formal education in film history, etc). 

Something interesting to consider would be the differences/correlation if we 
tested everybody who just left the theater about a certain movie. Since 
critics can be assumed to have a somewhat more uniform "film background," to
a certain extent, it could also be assumed that users who took the time to 
personally rate movies on iMDB also do not represent the average viewer's level
of interest or engagement with film in general. By sampling more people directly
at the source, we could have a more in-depth discussion regarding personal views
and film. 


## Methodology Part 2

Before getting started with part 2, we wanted to split up Action movies from 
Drama movies. The code below splits these two categories up, and then filters
out any movie that might be labeled as both an action movie and a drama movie. 
This decreased the amount of movies in our dataset from 877 to 596. These 596
are all categorized as either dramas or actions, but not both. We then 
created a new variable, critic_dif_fan, that showed the difference between
the critics view of a movie and the fans view of a movie numerically. This
will be used in our hypothesis testing to generate an outlook into the 
relationship between these variables. 


```{r separatingActionsAndDramas}
actionsAndDramas <- popularMovies %>%
  mutate(action = str_detect(Genre, "Action")) %>%
  mutate(drama = str_detect(Genre, "Drama")) %>%
  filter(!(action == drama))

```

```{r}
actionsAndDramas <- actionsAndDramas %>%
  mutate(critic_dif_fan = Metascore - newRating)

```

## Part 2: Hypothesis Testing for the Difference in Genre Preferences Between Fans and Critics


```{r load-data, message = F}

mean_critic_action <- actionsAndDramas %>% 
  filter(action == TRUE) %>% 
  summarise(mean_c_a = mean(Metascore, na.rm = TRUE)) %>% 
  pull()


mean_fan_action <- actionsAndDramas %>% 
  filter(action == TRUE) %>% 
  summarise(mean_c_a = mean(newRating, na.rm = TRUE)) %>% 
  pull()

diff_mean_action <- mean_critic_action - mean_fan_action
  
```



```{r diffInMeanAction ex-3}
set.seed(3)
null_dif_mean_action <- actionsAndDramas %>% 
  specify(response = critic_dif_fan, explanatory = action) %>% 
  hypothesise(null = "independence") %>% 
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("TRUE", "FALSE"))

 null_dif_mean_action %>% 
   get_p_value(obs_stat = diff_mean_action, direction = "both")
```


```{r}
visualize(null_dif_mean_action) +
  shade_p_value(obs_stat = diff_mean_action, direction = "both")
```




```{r actualDifferenceInMeansDrama}
mean_critic_drama <- actionsAndDramas %>% 
  filter(drama == TRUE) %>% 
  summarise(mean_c_a = mean(Metascore, na.rm = TRUE)) %>% 
  pull()


mean_fan_drama <- actionsAndDramas %>% 
  filter(drama == TRUE) %>% 
  summarise(mean_c_a = mean(newRating, na.rm = TRUE)) %>% 
  pull()

diff_mean_drama <- mean_critic_drama - mean_fan_drama
  
```



```{r diffInMeanDrama ex-3}
set.seed(3)
null_dif_mean_drama <- actionsAndDramas %>% 
  specify(response = critic_dif_fan, explanatory = drama) %>% 
  hypothesise(null = "independence") %>% 
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("TRUE", "FALSE"))

 null_dif_mean_drama %>% 
   get_p_value(obs_stat = diff_mean_drama, direction = "both")
```



```{r}
visualize(null_dif_mean_drama) +
  shade_p_value(obs_stat = diff_mean_drama, direction = "both")
```

## Part 2 Results and Discussion

There will be two separate null hypotheses for this part of the report.

The first null hypothesis is that there is no difference between the mean fan 
and critic views of action movies.

-   $H_0: \mu_{criticaction} - \mu_{fanaction} = 0$

The first alternative hypothesis is that there is a difference between the 
fan and critic views of action movies. 

-   $H_1: \mu_{criticaction} - \mu_{fanaction} \neq 0$

The second null hypothesis is that there is no difference between the fan and 
critic views of drama movies. 

-   $H_0: \mu_{criticdrama} - \mu_{fandrama} = 0$

The first alternative hypothesis is that there is a difference between the 
fan and critic views of drama movies. 

-   $H_1: \mu_{criticdrama} - \mu_{fandrama} \neq 0$



This simulation was conducted using 10000 repetitions for both in which the 
difference in means was tested. The p-value for both of these tests was 0, 
indicating that we can reject both null hypothesis. This means that there is
a difference between the fan and critic views for both action and drama movies.
What we found is that critics are harsher, on a "to-100" scale, for both dramas
and action movies relative to fans. However, critics much preferred dramas over
action movies as compared to fans, seeing as the observed statistic for the mean 
difference in action between critics and fans was -13.1 points, while the 
mean difference for dramas was -4.8 points. This can be seen graphically,
as in both representations of the distributions, our red line representing our
observed statistic is located to the left of our actual distribution. However,
that observed statistic was far closer to the distribution in the drama graph
as compared to the action graph. 

This logically seems to make sense. Building off of our previous explanations
of the "film background" of fans vs. critics, it would make sense that fans
might prefer a traditional blockbuster movie, as compared to a critic who might
prefer a slower-paced drama. Because critics might care more than fans about
more subtle aspects of film making such as cinematography, movies, 
such as dramas, that are slower, might focus on these aspects more and cater
to a critic's interest. 

