---
title: "April 20 - Turning in Final Report Document"
output: html_document
author: "Matthew Distell, Bo Aldridge, Haris Adnan, Lucan Franzblau, Devin Obee"
date: "4-19-2022"
---


## Load Packages 
```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse) 
library(tidymodels)
install.packages("readxl")
library("readxl")
``` 


# Load Data
```{r load-data, message = F}
myMovieData <- read_csv("IMDB-Movie-Data.csv")

```



## Introduction: Motivation and Context for the Research





## Dataset

```{r movie data}
glimpse(myMovieData)
```


## Research Questions




## Methodology

```{r popular movie filter}
popularMovies <- myMovieData %>% 
  filter(Votes >= 8000)
```

```{r IMDB}
popularMovies <- popularMovies %>% 
  mutate(newRating = Rating * 10)
```


## Part 1: The Relationship Between Fans vs. Critic Scoring and Box Office Revenue

```{r}
cor.test(popularMovies$newRating, popularMovies$`Revenue (Millions)`,
  method = "spearman"
)
```

```{r}
cor.test(popularMovies$Metascore, popularMovies$`Revenue (Millions)`,
  method = "spearman"
)
```



```{r linearReg}
model1 <- linear_reg() %>%
  set_engine("lm") %>%
  fit(`Revenue (Millions)` ~ newRating + Metascore, data = popularMovies)
tidy(model1)
```


The null hypothesis for each parameter is that each specific parameter does not
have a relationship with the total time this person spends awake at night.

The alternative hypothesis, on the other hand, is that each specific parameter 
does have a relationship with the total time this person spends awake at night.

The only predictor that was significant at the alpha level of .05 was Time To
Sleep, with a p-value of 3.2. * 10^-11 and a high t-value. 


```{r}
popularMovies %>% 
  ggplot(aes(x = newRating, y = `Revenue (Millions)`)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) 
  
```

```{r}
popularMovies %>% 
  ggplot(aes(x = Metascore, y = `Revenue (Millions)`)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) 
  
```

## Part 1 Results

## Part 1 Discussion

## Part 2: Hypothesis Testing for the Difference in Genre Preferences Between Fans and Critics


```{r separatingActionsAndDramas}
popularMovies <- popularMovies %>%
  mutate(action = str_detect(Genre, "Action")) %>%
  mutate(drama = str_detect(Genre, "Drama")) %>%
  filter(!(action == drama))

```

```{r}
popularMovies <- popularMovies %>%
  mutate(critic_dif_fan = Metascore - newRating)

```

```{r load-data, message = F}

mean_critic_action <- popularMovies %>% 
  filter(action == TRUE) %>% 
  summarise(mean_c_a = mean(Metascore, na.rm = TRUE)) %>% 
  pull()


mean_fan_action <- popularMovies %>% 
  filter(action == TRUE) %>% 
  summarise(mean_c_a = mean(newRating, na.rm = TRUE)) %>% 
  pull()

diff_mean_action <- mean_critic_action - mean_fan_action
  
```



```{r diffInMeanAction ex-3}
set.seed(3)
null_dif_mean_action <- popularMovies %>% 
  specify(response = critic_dif_fan, explanatory = action) %>% 
  hypothesise(null = "independence") %>% 
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("TRUE", "FALSE"))

 null_dif_mean_action %>% 
   get_p_value(obs_stat = diff_mean_action, direction = "both")
```


```{r}
visualize(null_dif_mean_action) +
  shade_p_value(obs_stat = diff_mean_action, direction = "both")
```




```{r actualDifferenceInMeansDrama}
mean_critic_drama <- popularMovies %>% 
  filter(drama == TRUE) %>% 
  summarise(mean_c_a = mean(Metascore, na.rm = TRUE)) %>% 
  pull()


mean_fan_drama <- popularMovies %>% 
  filter(drama == TRUE) %>% 
  summarise(mean_c_a = mean(newRating, na.rm = TRUE)) %>% 
  pull()

diff_mean_drama <- mean_critic_drama - mean_fan_drama
  
```



```{r diffInMeanDrama ex-3}
set.seed(3)
null_dif_mean_drama <- popularMovies %>% 
  specify(response = critic_dif_fan, explanatory = drama) %>% 
  hypothesise(null = "independence") %>% 
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("TRUE", "FALSE"))

 null_dif_mean_drama %>% 
   get_p_value(obs_stat = diff_mean_drama, direction = "both")
```



```{r}
visualize(null_dif_mean_drama) +
  shade_p_value(obs_stat = diff_mean_drama, direction = "both")
```

## Part 2 Results

## Part 2 Discussion