---
title: "First Draft"
author: "Matthew Distell, Bo Aldridge, Haris Adnan, Lucan Franzblau, Devin Obee"
date: "2-25-2022"
output:
  pdf_document: default
  word_document: default
subtitle: 'due February 25, 2022 by 11:59 PM '
---


# Introduction: Motivation, Context, and our Question for Research


Ever since film itself became popularized in Western Culture at the beginning of
the 20th century, it has stood as one of the most popular forms of artistic 
creativity and expression. As such, the medium itself is able to showcase 
a wide variety of different subplots, themes, and genres. However, many movies 
today and historically follow a very similar pattern in the hopes of maximizing 
revenue and viewership. My research group and I are interested in what exactly
drives acclaim and viewership for fans as compared to critics. We believe that
critics view films in a different manner than fans, such that their criteria 
for "success" is far different from that of a fan reviewer. We also believe that 
these differences can be specified and categorically discussed through areas such
as genre, length, and country of origin. Our hypothesis is that lower budget movies
will, on average, perform better in critic reviews than fan reviews, and vice versa. 






# Load Packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse) 
library(tidymodels)
install.packages("readxl")
library("readxl")
``` 


# Load Data
```{r load-data, message = F}
myMovieData <- read_csv("IMDB-Movie-Data.csv")

```

# Glimpse

Please use `glimpse` for your datasets here.
```{r}
glimpse(myMovieData)

```
```{r popular}
popularMovies <- myMovieData %>% 
  filter(Votes >= 10000)
```



```{r linearReg}
model1 <- linear_reg() %>% 
  set_engine("lm") %>% 
  fit(`Revenue (Millions)` ~ Rating + Metascore, data = popularMovies) 
tidy(model1)
```



# Results:Analyzing Genre vs. Critic and Fan Rating


```{r separatingActionsAndDramas}
popularMovies <- popularMovies %>% 
  mutate(action = str_detect(Genre, "Action")) %>% 
  mutate(drama = str_detect(Genre, "Drama")) %>% 
  filter(!(action == drama))

```



# Discussion

As showcased above, there is a clear and noticeable difference between the critic
rating of a movie (Metacritic) vs. the fan's rating of a movie (iMDB Rating) with 
regards to box office success. Critics, on average, tend to prefer movies of 
all types of box office success. This could be because critics have viewed more 
movies across their lifetime, and, as such, look for different characteristics 
in a film than the average fan. The average fan, on the other hand, might be more
invested in a huge blockbuster series, such as Star Wars, for instance, where 
the high rating could also be attributed to a general "cult following" mindset 
rather to a strict review of the quality of the film. 
