---
title: "First Draft"
author: "Matthew Distell, Bo Aldridge, Haris Adnan, Lucan Franzblau, Devin Obee"
date: "2-25-2022"
output:
  pdf_document: default
  word_document: default
subtitle: 'due February 25, 2022 by 11:59 PM '
---
# Load Packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse) 
install.packages("readxl")
library("readxl")
``` 
# Load Data
```{r load-data, message = F}
myMovieData <- read_csv("IMDB-Movie-Data.csv")
myNBAData <- read_csv("nba.games.stats.csv")
myMusicData <- read_excel("Hot 100 Audio Features.xlsx")
```
# Introduction and Data
Please introduce and discuss your data here.

For our three datasets, we are using data called myMovieData, myMusicData, and
myNBAData. MyMovieData is collected from IMDB, or the International Movie 
Database. On that website, there is data listed for 1000 movies about 12 
different variables, including genre, director, year released, runtime, and 
audience rating. MyMusicData is collected from the Billboard100 Hot Charts 
that features 29503 songs featured on the chart. The variables in the set
include the runtime, loudness, performer, and genre of a given song. Finally, 
our myNbaData set analyzes the results of 9840 NBA games played from 2014-2018.
This dataset includes statistics such as Field Goal Percentage, Three Point 
Percentage, who the home team was, and rebounding. 

# Research Questions
Please discuss your research questions here.

For each of these three datasets, we have specific research questions designed
to answer interesting questions. For the myMovieData set, we plan on analyzing
the differences between critic reviews and fan reviews, and identify any trends
within that framework. More generally, our question is posed as: What do critics
prefer in a movie as compared to fans? Our brief hypothesis is that fans prefer
more action/adventure movies with shorter runtimes, while critics prefer longer
dramas. 
 

# Glimpse

Please use `glimpse` for your datasets here.
```{r}
glimpse(myMovieData)

```
Does revenue increase along with rating? 

Visualize how revenue varies by year? Which year collected the most revenue 

Possible question: What is the probability that the metascore is the exact same as the rating?

What is the probability a randomly selected movie has a rating over 7.0?
